---
title: "Final Project"
author: "William Hyltin, Holly Milazzo, Tim Harrison"
format: html
---

some dataset options:  

**Linear Regression**  

1. https://www.kaggle.com/datasets/tawfikelmetwally/advertising-dataset  
2. https://www.kaggle.com/datasets/mohannapd/mobile-price-prediction  
3. https://www.kaggle.com/datasets/midhundasl/co2-emission-of-cars-dataset  

**Logistic Regression**  
 
 1. https://www.kaggle.com/datasets/kandij/diabetes-dataset  
 2. https://www.kaggle.com/datasets/marshuu/breast-cancer  
 3. https://www.kaggle.com/datasets/alexandrepetit881234/fake-bills  
 4. https://www.kaggle.com/datasets/vikasukani/loan-eligible-dataset  
 

From what i've seen I like the cell phone price prediction dataset and the loan eligibility dataset. Both are relatively small, and we've been primarily working with small datasets for his class, and since he's very focused on the statistical methods and tests large datasets will likely cause problems for us.
 
```{r}
pacman::p_load(tidyverse, here, skimr)
```
 
```{r}
loan_df <- read.csv(here('loan-test.csv'))
cell_phones_df <- read.csv(here('Cellphone.csv'))
```

I used the given test set for the loan dataset because it's smaller and we won't need to do a train-test split for this class anyway.

```{r}
loan_df %>% head()
```

```{r}
cell_phones_df %>% head()
```

```{r}
plot(select_if(loan_df, is.numeric))
```

```{r}
plot(select_if(cell_phones_df, is.numeric))
```

Basically illegible, there's so many variables we'll likely need to do variable selection early on (qualitatively rather than quantitatively).

```{r}
skim(cell_phones_df)
```

```{r}
skim(loan_df)
```

Loan has some missing variables, but nothing so bad we couldn't justify filtering or imputing or something.


Still early on, but right now I like either of these two, and I'm pretty impartial to either one.